### 2014-09-29 doc/thesis/typedlua.tex
Fixing evaluation to include methods from userdata

The following example shows the description file for \texttt{lmd5} \citep{lmd5},
a MD5 digest library for Lua that is written in C:
\begin{verbatim}
    userdata md5_context
      __tostring : (self) -> (string)
      clone : (self) -> (self)
      digest : (self|string, value?) -> (string)
      new : () -> (self)
      reset : (self) -> (self)
      update : (self, string*) -> (self)
      version : string
    end

>>>>

The following example shows the description file for \texttt{lmd5} \citep{lmd5},
a MD5 digest library for Lua that is written in C:
\begin{verbatim}
    userdata md5_context
      __tostring : (self) -> (string)
      clone : (self) -> (self)
      digest : (self, value) -> (string)
      new : (self) -> (self)
      reset : (self) -> (self)
      update : (self, string*) -> (self)
    end
